Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-06-04 paper/main.tex
Auto Update from local Sharelatex

There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers from data, grouping individuals, and similar anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.

@@

@@

% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
% why not full synthesize a full dataset? limited to sql query where relevant data is brought together, easier to model 1 table than lots of separate tables. Modelling lots of separate tables requires extensive meta data configuration and a significant amount of computing power to generate...
% where to put this text? "Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."

>>>>

There is a large body of published literature detailing methods for overcoming this difficulty related to data via de-identification (removing key identifiers, grouping individuals, and related anonymization techniques \cite{hippapro}) and synthesizing data (creating data through algorithmic means, population level statistics, randomization, and ideally preserving inter-relationships between records \cite{walonoski_synthea_2018, patki_synthetic_2016, choi_generating_2017}), however at present a mechanism to routinely \emph{use} these techniques has not been forthcoming.

@@

% previously had some information about various data anonymization and synthesis techniques. Put that back?

@@

% some text about goal to make our research reproducible/replicable - provide source code, pip/conda environment files, docker container
% explain why not full synthesize a full dataset. better to limit to sql query where relevant data is brought together; easier to model 1 table than lots of separate tables. Modelling lots of separate tables requires extensive meta data configuration and a significant amount of computing power to generate...
% where to put this text? "Unit testing is important but often overlooked - unit tests can show how a researcher validated their code was giving expected results which can often lead to insights not normally communicated in a results section of a journal article."
